Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-10-21 paper/ms.tex
some updates in the paper

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field size by
constructing mock fields from a large cosmological N-body
simulation matching the geometries of observed fields. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm   min}<M_{\rm h}<M_{\rm max}$ can only host
one detectable LAE with a probability $f_{\rm occ}$. The main motivation to
build such a model is to avoid the large uncertainties in the estimation of
\ly luminosities. We find that the clustering and number density information are
insufficient to impose a tight constraint on the escape fraction. On
the other hand the minimum mass and maximum mass are tightly
constrained to be $M_{\rm max}<10^{12}$\hMsun and
$10^{10}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$.  We also find
that all models have a narrow mass range $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than $1.0$ dex,
with the vast majority in the range $\Delta M<0.5$ dex. Already
published constraints on the mass range and occupation fraction are a sub-set of
the models we report in this \documentname. Our results present an
inconclusive response as to which is the occupation fraction for LAEs
at $z=3.1$. A precise answer requires robust physical models for the
connection between dark matter, star formation and the escape of \ly
radiation. That kind of modelling should also be able to provide a
plausible explanation for the narrow range in mass $\Delta M<1.0$ dex
derived here for the halos hosting LAEs at $z=3.1$.

@@

The second constraint is the angular correlation function
(ACF). \cite{Yamada2012} does not report an ACF measurement. Instead
we use the results by \cite{Hayashino2004} and
\cite{Ouchi2008,Ouchi2010}. \cite{Hayashino2004} observed in the
densest field of SSA22 while \cite{Ouchi2008} observed on a $\sim 0.5$
deg$^2$ field.  There are some differences between these
observations and those by \cite{Yamada2012}. The details in the color
selection, corresponding limiting luminosities and EW thresholds are
different in these references. Nevertheless we use the ACF from these
observations as additional constraints in spite of the fact that the
first selected models are based only on the surface density statistics by
\cite{Yamada2012}.

>>>>

\begin{abstract}
%
We derive constraints on the mass and occupation fraction of dark
matter halos hosting \ly Emitting galaxies (LAEs) at a redshift of
$z=3.1$ by matching the number density and the angular
correlation function between mock and observed fields. We explicitly
take into account the cosmic variance on the typical observed field size by
constructing mock fields from a large cosmological N-body
simulation matching the geometries of observed fields. To populate the
halos in the simulation we use a model where a dark matter halo with
mass in the range $M_{\rm   min}<M_{\rm h}<M_{\rm max}$ can only host
one detectable LAE with a probability $f_{\rm occ}$. The main motivation to
build such a model is to avoid the large uncertainties in the estimation of
\ly luminosities. We find that the clustering and number density information are
insufficient to impose a tight constraint on the {\bf occupation} fraction. On
the other hand the minimum mass and maximum mass are tightly
constrained to be $M_{\rm max}<10^{12}$\hMsun and
$10^{10}\hMsun\leq M_{\rm min}\leq 10^{11.5}\hMsun$.  We also find
that all models have a narrow mass range $\Delta M \equiv
\log_{10}M_{\rm max} - \log_{10} M_{\rm min}$ smaller than $1.0$ dex,
with the vast majority in the range $\Delta M<0.5$ dex. Already
published constraints on the mass range and occupation fraction are a sub-set of
the models we report in this \documentname. Our results present an
inconclusive response as to which is the occupation fraction for LAEs
at $z=3.1$. A precise answer requires robust physical models for the
connection between dark matter, star formation and the escape of \ly
radiation. That kind of modelling should also be able to provide a
plausible explanation for the narrow range in mass $\Delta M<1.0$ dex
derived here for the halos hosting LAEs at $z=3.1$.

@@

The second constraint is the angular correlation function
(ACF). {\bf \cite{Yamada2012} does not report an ACF measurement}. Instead
we use the results by \cite{Hayashino2004} and
\cite{Ouchi2008,Ouchi2010}. \cite{Hayashino2004} observed in the
densest field of SSA22 while \cite{Ouchi2008} observed a 1 deg$^2$
over the SXDS field, which is twice as large as the SXDS region
observed by \cite{Yamada2012}.

There are some differences between these observations and those by
\cite{Yamada2012}. The details in the color selection, corresponding
limiting luminosities and EW thresholds are different in these
references. Nevertheless we use the ACF from these observations as
additional constraints in spite of the fact that the first selected
models are based only on the surface density statistics by \cite{Yamada2012}.

{\bf The LAEs number density inferred by \cite{Hayashino2004} is
  $0.37$ arcmin$^{-2}$, which is $15\%$ lower than the new measurement
by \cite{Yamada2012}. In the case of \cite{Ouchi2008} the number
density is $0.10$ arcmin$^{-2}$, which is $\sim 50\%$ than the value
inferred by \cite{Yamada2012} for a portion of the same region.}
